The \textit{Kepler} Smear Campaign

### 2019-03-17 paper/ms.tex
aerts changes

The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18,2018arXiv180907779A}. These studies cover about 70 stars so far. However, the vast majority of intermediate-mass stars observed by Kepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties. One of the valuable outputs of our current work includes the reduced light curves of several early-B stars, which were only scarcely targeted in the nominal \kepler mission. The few that were monitored did not reveal suitable oscillation frequency patterns to achieve a unique mode identification, which is a requirement to perform asteroseismic modelling. The investigation of pulsation modes in high-mass stars using high-quality \kepler smear data combined with high-precision spectroscopy to identify the modes \citep[Chapter 6]{aertsbook} is an exciting prospect for asteroseismology, as the interior physics of these stars are largely unknown, yet they play a pivotal role in stellar and galactic evolution. The in-depth asteroseismic analysis of the smear data for the~B~stars will be the subject of future work.

>>>>

The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18,2018arXiv180907779A,2018A&A...618A..47C,2019MNRAS.482.1757L}. These studies cover about 100 stars so far and many more are to come. For 37 of the F-type pulsators among those, asteroseismic modelling of the g modes led to their masses, ages, core rotation and core mass with relative precisions of about 10\% \citep{2019MNRAS.tmp..495M}. The vast majority of B-type intermediate-mass stars observed byKepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties. However, the vast majority of intermediate-mass stars observed by Kepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties. One of the valuable outputs of our current work includes the reduced light curves of several early-B stars, which were only scarcely targeted in the nominal \kepler mission. The few that were monitored did not reveal suitable oscillation frequency patterns to achieve a unique mode identification, which is a requirement to perform asteroseismic modelling. The investigation of pulsation modes in high-mass stars using high-quality \kepler smear data combined with high-precision spectroscopy to identify the modes \citep[Chapter 6]{aertsbook} is an exciting prospect for asteroseismology, as the interior physics of these stars are largely unknown, yet they play a pivotal role in stellar and galactic evolution. The in-depth asteroseismic analysis of the smear data for the~B~stars will be the subject of future work.
